Illustrating Good Practice in {\LaTeX}

### 2021-07-09 articles/good_practice.tex
new articles

@@

Nicholas Kostin \\
\url{https://github.com/nkostin4}

@@

This document is not meant to be a guide on how to use {\LaTeX}, since plenty of those already exist. Rather, what follows is an incoherent collection of examples that demonstrate good practice. Be sure to visit \url{https://github.com/nkostin4/LaTeX-templates} for more.

@@

These circled numbers work in equations too!

\begin{equation*}
    \Scale[6]{\circled{4}{TEAL}{RED}{BLACK} + \circled{4}{TEAL}{RED}{BLACK} = \circled{8}{TEAL}{RED}{BLACK}}
\end{equation*}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}
    \coordinate (vertex1) at (4,0);
    \coordinate (vertex2) at (2,3.464102);
    \coordinate (vertex3) at (-2,3.464102);
    \coordinate (vertex4) at (-4,0);
    \coordinate (vertex5) at (-2,-3.464102);
    \coordinate (vertex6) at (2,-3.464102);
    %
    \node at (vertex1) (nodeV1) {\Huge\circled{1}{DARKBLUE}{red}{red}};
    \node at (vertex2) (nodeV2) {\Huge\circled{2}{DARKBLUE}{red}{red}};
    \node at (vertex3) (nodeV3) {\Huge\circled{3}{DARKBLUE}{red}{red}};
    \node at (vertex4) (nodeV4) {\Huge\circled{4}{DARKBLUE}{red}{red}};
    \node at (vertex5) (nodeV5) {\Huge\circled{5}{DARKBLUE}{red}{red}};
    \node at (vertex6) (nodeV6) {\Huge\circled{6}{DARKBLUE}{red}{red}};
    %
    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV2);
    \draw[black, ultra thick, ->] (nodeV2) -- (nodeV3);
    \draw[black, ultra thick, <->] (nodeV3) -- (nodeV4);
    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV5);
    \draw[black, ultra thick, <->] (nodeV5) -- (nodeV6);
    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV4);
    \draw[black, ultra thick, ->] (nodeV1) -- (nodeV3);
    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV6);
\end{tikzpicture}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}[scale=1.2]
    % primary colors
    \fill[BLUE] (30:2.4) circle (4);
    \fill[RED] (150:2.4) circle (4);
    \fill[GREEN] (270:2.4) circle (4);
    % secondary colors
    \begin{scope} % red + blue = purple
        \clip (150:2.4) circle (4);
        \fill[PURPLE] (30:2.4) circle (4);
    \end{scope}
    \begin{scope} % red + green = yellow
        \clip (270:2.4) circle (4);
        \fill[YELLOW] (150:2.4) circle (4);
    \end{scope}
    \begin{scope} green + blue = teal
        \clip (30:2.4) circle (4);
        \fill[TEAL] (270:2.4) circle (4);
    \end{scope}
    % red + blue + green = white
    \begin{scope}
        \clip (30:2.4) circle (4);
        \clip (150:2.4) circle (4);
        \fill[WHITE] (270:2.4) circle (4);
    \end{scope}
\end{tikzpicture}
\end{figure}

>>>>

\title{Illustrating Good Practice in {\LaTeX}}
\author{Nicholas D. Kostin}
\date{July 2021}

@@

\maketitle

@@

This document is not meant to be a guide on how to use {\LaTeX}, since plenty of those already exist. Rather, what follows is an incoherent collection of examples that illustrate good practice. For more of my awesome {\LaTeX} resources, visit \url{https://github.com/nkostin4/LaTeX-templates}.

@@

These circled numbers work in equations too!
\begin{equation*}
    \bigints_{\circled{$a$}{PINK}{BLACK}{BLACK}}^{\circled{$b$}{GOLDC}{BLACK}{BLACK}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{+} \hspace{1em} \bigints_{\circled{$b$}{GOLDC}{BLACK}{BLACK}}^{\circled{$a$}{PINK}{BLACK}{BLACK}} \Scale[2]{f(x)} \Scale[2]{dx} \hspace{1em} \Scale[2]{=} \hspace{1em} \Scale[2]{\circled{0}{GREEN}{RED}{BLACK}}
\end{equation*}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}
    \coordinate (vertex1) at (4,0);
    \coordinate (vertex2) at (2,3.464102);
    \coordinate (vertex3) at (-2,3.464102);
    \coordinate (vertex4) at (-4,0);
    \coordinate (vertex5) at (-2,-3.464102);
    \coordinate (vertex6) at (2,-3.464102);
    %
    \node at (vertex1) (nodeV1) {\Huge\circled{1}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex2) (nodeV2) {\Huge\circled{2}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex3) (nodeV3) {\Huge\circled{3}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex4) (nodeV4) {\Huge\circled{4}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex5) (nodeV5) {\Huge\circled{5}{ORANGE}{RED}{DARKBLUE}};
    \node at (vertex6) (nodeV6) {\Huge\circled{6}{ORANGE}{RED}{DARKBLUE}};
    %
    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV2);
    \draw[black, ultra thick, ->] (nodeV2) -- (nodeV3);
    \draw[black, ultra thick, <->] (nodeV3) -- (nodeV4);
    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV5);
    \draw[black, ultra thick, <->] (nodeV5) -- (nodeV6);
    \draw[black, ultra thick, <->] (nodeV1) -- (nodeV4);
    \draw[black, ultra thick, ->] (nodeV1) -- (nodeV3);
    \draw[black, ultra thick, ->] (nodeV4) -- (nodeV6);
\end{tikzpicture}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}[scale=0.75]
    % primary colors
    \fill[BLUE] (30:2.4) circle (4);
    \fill[RED] (150:2.4) circle (4);
    \fill[GREEN] (270:2.4) circle (4);
    % secondary colors
    \begin{scope} % red + blue = purple
        \clip (150:2.4) circle (4);
        \fill[PURPLE] (30:2.4) circle (4);
    \end{scope}
    \begin{scope} % red + green = yellow
        \clip (270:2.4) circle (4);
        \fill[YELLOW] (150:2.4) circle (4);
    \end{scope}
    \begin{scope} green + blue = teal
        \clip (30:2.4) circle (4);
        \fill[TEAL] (270:2.4) circle (4);
    \end{scope}
    % red + blue + green = white
    \begin{scope}
        \clip (30:2.4) circle (4);
        \clip (150:2.4) circle (4);
        \fill[WHITE] (270:2.4) circle (4);
    \end{scope}
\end{tikzpicture}
\end{figure}
